---
dataMaid: yes
title: Prueba_adres_ilich
subtitle: "análisis exploratorio y visualización"
date: 2024-02-03 18:18:41.556213
output: html_document
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```

```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```

# Data report overview
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations     504660

Number of variables            74
---------------------------------




### Checks performed
The following variable checks were performed, depending on the data type of each variable:

-----------------------------------------------------------------------------------------------------------------------------------------------
&nbsp;                                                 character   factor    labelled   haven labelled   numeric   integer   logical    Date   
----------------------------------------------------- ----------- --------- ---------- ---------------- --------- --------- --------- ---------
Identify miscoded missing values                        &times;    &times;   &times;       &times;       &times;   &times;             &times; 

Identify prefixed and suffixed whitespace               &times;    &times;   &times;       &times;                                             

Identify levels with < 6 obs.                           &times;    &times;   &times;       &times;                                             

Identify case issues                                    &times;    &times;   &times;       &times;                                             

Identify misclassified numeric or integer variables     &times;    &times;   &times;       &times;                                             

Identify outliers                                                                                        &times;   &times;             &times; 
-----------------------------------------------------------------------------------------------------------------------------------------------




Please note that all numerical values in the following have been rounded to 2 decimals.


# Summary table

----------------------------------------------------------------------------------------------------------------------------------------------------------
&nbsp;                                                                           Variable class     # unique values   Missing observations  Any problems? 
-------------------------------------------------------------------------------- ---------------- ----------------- ---------------------- ---------------
[ano]                                                                            numeric                          7                 0.00 %                

[Clase]                                                                          character                        2                 0.00 %                

[Pertenencia\_Etnica]                                                            character                        6                 0.00 %                

[Pertenencia\_Etnica\_Agregada]                                                  character                        2                 0.00 %                

[Estrato]                                                                        character                        7                 0.00 %                

[Colegio\_Caracter]                                                              character                        2                96.48 %     &times;    

[Region]                                                                         character                       10                 5.25 %                

[Region\_DANE]                                                                   character                        7                 5.25 %                

[Departamento]                                                                   character                       34                 5.25 %                

[cod\_dpto]                                                                      numeric                         34                 5.25 %     &times;    

[Sexo]                                                                           character                        2                 0.00 %                

[Grupo\_Decenal\_Edad]                                                           character                       10                 0.00 %                

[Regimen\_Afiliacion\_p6100]                                                     character                        5                 6.32 %                

[Departamento\_Co]                                                               character                       34                 0.00 %                

[Quintil\_Ingreso\_Percapita]                                                    character                        5                 0.00 %                

[Quintil\_Ingreso\_Percapita\_Clase]                                             character                        5                 0.00 %                

[fex\_c]                                                                         numeric                      87023                 0.00 %     &times;    

[Accion\_Tratar\_enfermedad\_P8563]                                              character                        9                92.70 %                

[Accion\_Tratar\_enfermedad\_agregada\_P8563]                                    character                        4                92.70 %                

[No\_Asistencia\_Razon\_p6153]                                                   character                       14                97.49 %                

[No\_Asistencia\_Agregada\_p6153]                                                character                        3                97.41 %                

[No\_Afiliacion\_Razon\_p768]                                                    character                        9                95.15 %                

[Dias\_incapacidad\_p6134]                                                       numeric                         71                91.14 %     &times;    

[Ocupacion\_p6240]                                                               character                        7                20.22 %                

[Ocupacion\_Posicion\_p6435]                                                     character                       11                57.00 %                

[Estado\_salud\_general\_P6127]                                                  character                        4                 0.00 %                

[calidad\_Atencion\_Prevencion\_P8595]                                           character                        5                59.67 %                

[Enfermedad\_Ultimo\_mes\_P5665]                                                 character                        2                 0.00 %                

[Cubrir\_Costos\_Atención\_Salud\_EPS\_p8556s1]                                  character                        3                91.14 %                

[Cubrir\_Costos\_Atencion\_Salud\_Seguro\_Voluntario\_p8556s2]                   character                        3                91.14 %                

[Cubrir\_Costos\_Atencion\_Salud\_Seguro\_Obligatorio\_p8556s4]                  character                        3                91.14 %                

[Cubrir\_Costos\_Atencion\_Salud\_Alcaldia\_p8556s5]                             character                        3                91.14 %                

[Cubrir\_Costos\_Atencion\_Salud\_Propios\_familiares\_p8556s6]                  character                        3                91.14 %                

[Cubrir\_Costos\_Atencion\_Salud\_Otras\_Personas\_p8556s9]                      character                        3                91.14 %                

[Cubrir\_Costos\_Atencion\_Salud\_No\_Requiere\_p8556s10]                        character                        3                91.14 %                

[Percepcion\_Calidad\_Entidad\_p6181]                                            character                        6                 6.48 %                

[Percepcion\_Calidad\_Entidad\_Factor\_P798]                                     character                        8                88.02 %                

[Percepcion\_Calidad\_Prestacion\_p8554]                                         logical                          1               100.00 %     &times;    

[Percepcion\_Calidad\_Prestacion\_Factor\_P801]                                  character                        9                99.49 %                

[Percepcion\_pobreza\_p5230]                                                     character                        3                 0.01 %                

[Percepcion\_suficiencia\_ingresos\_p9090]                                       character                        4                 0.01 %                

[Quejas\_Ultimo\_Ano]                                                            character                        3                63.57 %                

[Tutelas\_Ultimo\_Ano]                                                           character                        3                 0.01 %                

[Tutelas\_Ultimo\_Ano\_razon]                                                    character                        8                98.42 %                

[Cronica\_Diagnostico\_p1930]                                                    character                        3                77.63 %                

[Cronica\_Tratamiento\_p1930s1]                                                  character                        3                96.85 %                

[Discapacidad\_Oir\_p1906s1]                                                     character                        5                72.38 %                

[Consulta\_Prevencion\_Medico]                                                   character                        3                57.64 %                

[Consulta\_Prevencion\_Odontologo]                                               character                        3                57.64 %                

[Consulta\_Prevencion\_Medico\_Odontologo]                                       character                        5                42.36 %                

[Discapacidad\_Hablar\_p1906s2]                                                  character                        5                72.38 %                

[Discapacidad\_Ver\_p1906s3]                                                     character                        5                72.38 %                

[Discapacidad\_Moverse\_Caminar\_p1906s4]                                        character                        5                72.38 %                

[Discapacidad\_Usar\_Manos\_p1906s5]                                             character                        5                72.38 %                

[Discapacidad\_Entender\_p1906s6]                                                character                        5                72.38 %                

[Discapacidad\_Comer\_Vestirse\_Bañarse\_Solo\_p1906s7]                          character                        5                72.38 %                

[Discapacidad\_Relacionarse\_p1906s8]                                            character                        5                72.38 %                

[Dias\_Cita\_consulta\_Acudio\_especialista\_p6199]                              logical                          1               100.00 %     &times;    

[Dias\_Cita\_consulta\_Medico\_p6199]                                            numeric                         29                97.10 %                

[Dias\_Cita\_consulta\_Odontologo\_p6199]                                        numeric                         22                99.73 %                

[Algun\_miembro\_Hogar\_No\_Consumio\_Ninguna\_Comida\_Un\_Dia\_O\_Mas\_p8706]   character                        3                14.71 %                

[Controles\_Crecimiento\_Desarrollo\_p6161]                                      character                        3                97.48 %                

[Controles\_Crecimiento\_Desarrollo\_numero\_p6161]                              numeric                         19                97.74 %     &times;    

[Alfabeta\_p6160]                                                                character                        3                 7.62 %                

[Asiste\_Educacion\_p8586]                                                       character                        3                 7.62 %                

[Razon\_No\_Estudio\_p6218]                                                      character                       16                77.46 %     &times;    

[Razon\_No\_Estudio\_Agregada\_p6218]                                            character                        3                77.46 %                

[Nivel\_Educativo\_Actual\_p8587]                                                character                       14                34.88 %                

[Nivel\_Educativo\_Alcanzado\_p1088]                                             character                        9                72.75 %                

[Anos\_de\_Educacion]                                                            numeric                         32                 0.00 %                

[Anos\_de\_Educacion.jefe]                                                       numeric                         32                 0.00 %                

[Analfabetismo\_IPM]                                                             character                        2                 0.00 %                

[Rezago\_Escolar\_IPM]                                                           character                        3                79.24 %                

[Inasistencia\_Escolar\_IPM]                                                     character                        3                79.35 %                
----------------------------------------------------------------------------------------------------------------------------------------------------------




# Variable list
## ano

<div class = "row">
<div class = "col-lg-8">

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values              7

Median                            2015

1st and 3rd quartiles       2013; 2017

Min. and max.               2012; 2018
--------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-1-ano', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(2012, 2012.5, 2013, 
2013.5, 2014, 2014.5, 2015, 2015.5, 2016, 2016.5, 2017, 2017.5
), xmax = c(2012.5, 2013, 2013.5, 2014, 2014.5, 2015, 2015.5, 
2016, 2016.5, 2017, 2017.5, 2018), ymin = c(0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(74172L, 73155L, 0L, 67548L, 0L, 76026L, 
0L, 74349L, 0L, 26500L, 0L, 112910L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "ano")
```

</div>
</div>




---

## Clase

<div class = "row">
<div class = "col-lg-8">

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                character

Number of missing obs.         0 (0 %)

Number of unique values              2

Mode                        "Cabecera"
--------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-2-Clase', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Cabecera", 
"Centros poblados, inspección de policía o corregimientos"), class = "factor"), 
    y = c(312485L, 192175L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Clase")
```

</div>
</div>




---

## Pertenencia\_Etnica

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------------------
Feature                                          Result
------------------------- -----------------------------
Variable type                                 character

Number of missing obs.                          0 (0 %)

Number of unique values                               6

Mode                        "Ninguno de los anteriores"
-------------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-3-Pertenencia-Etnica', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:6, levels = c("Gitano (rom)", 
"Indígena", "Negro, mulato (afrodescendiente)", "Ninguno de los anteriores", 
"Palenquero", "Raizal del archipiélago"), class = "factor"), 
    y = c(102L, 30673L, 63699L, 406381L, 240L, 3565L)), class = "data.frame", row.names = c(NA, 
-6L)), vnam = "Pertenencia_Etnica")
```

</div>
</div>




---

## Pertenencia\_Etnica\_Agregada

<div class = "row">
<div class = "col-lg-8">

----------------------------------------------------
Feature                                       Result
------------------------- --------------------------
Variable type                              character

Number of missing obs.                       0 (0 %)

Number of unique values                            2

Mode                        "Sin Pertenencia étnica"
----------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-4-Pertenencia-Etnica-Agregada', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Con Pertenencia étnica", 
"Sin Pertenencia étnica"), class = "factor"), y = c(98279L, 
406381L)), class = "data.frame", row.names = c(NA, -2L)), vnam = "Pertenencia_Etnica_Agregada")
```

</div>
</div>




---

## Estrato

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.               0 (0 %)

Number of unique values                    7

Mode                        "1. Bajo - Bajo"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-5-Estrato', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:7, levels = c("0. Sin estrato", 
"1. Bajo - Bajo", "2. Bajo", "3. Medio - Bajo", "4. Medio", "5. Medio - Alto", 
"6. Alto"), class = "factor"), y = c(28992L, 221783L, 173011L, 
62653L, 11957L, 3907L, 2357L)), class = "data.frame", row.names = c(NA, 
-7L)), vnam = "Estrato")
```

</div>
</div>




---

## Colegio\_Caracter

* The variable only takes one (non-missing) value: \"Oficial\". The variable contains 96.48 \% missing observations.



---

## Region

<div class = "row">
<div class = "col-lg-8">

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                    character

Number of missing obs.      26500 (5.25 %)

Number of unique values                  9

Mode                           "Atlántica"
------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-7-Region', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:9, levels = c("Antioquia", 
"Atlántica", "Bogotá", "Central", "Oriental", "Orinoquía - Amazonia", 
"Pacífica (sin Valle)", "San Andrés, Providencia y Santa Catalina", 
"Valle del Cauca"), class = "factor"), y = c(51593L, 89281L, 
32108L, 71050L, 66422L, 27095L, 65638L, 9999L, 64974L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "Region")
```

</div>
</div>




---

## Region\_DANE

<div class = "row">
<div class = "col-lg-8">

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                    character

Number of missing obs.      26500 (5.25 %)

Number of unique values                  6

Mode                            "Pacífica"
------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-8-Region-DANE', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:6, levels = c("Amazonía", 
"Caribe", "Central", "Eje Cafetero - Antioquia", "Llanos - Orinoquía", 
"Pacífica"), class = "factor"), y = c(23306L, 99280L, 100304L, 
100572L, 24086L, 130612L)), class = "data.frame", row.names = c(NA, 
-6L)), vnam = "Region_DANE")
```

</div>
</div>




---

## Departamento

<div class = "row">
<div class = "col-lg-8">

---------------------------------------------
Feature                                Result
------------------------- -------------------
Variable type                       character

Number of missing obs.         26500 (5.25 %)

Number of unique values                    33

Mode                        "Valle del Cauca"
---------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-9-Departamento', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:33, levels = c("Amazonas", 
"Antioquía", "Arauca", "Atlántico", "Bogotá", "Bolívar", 
"Boyacá", "Caldas", "Caquetá", "Casanare", "Cauca", "Cesar", 
"Choco", "Córdoba", "Cundinamarca", "Guainía", "Guaviare", 
"Huila", "La Guajira", "Magdalena", "Meta", "Nariño", "Norte de Santander", 
"Putumayo", "Quindío", "Risaralda", "San Andrés, Providencia y Santa Catalina", 
"Santander", "Sucre", "Tolima", "Valle del Cauca", "Vaupés", 
"Vichada"), class = "factor"), y = c(3202L, 51593L, 5920L, 16283L, 
32108L, 14424L, 15218L, 13139L, 9299L, 5839L, 27269L, 11663L, 
11927L, 14674L, 17000L, 735L, 2999L, 12772L, 8706L, 13183L, 10998L, 
26442L, 11086L, 4853L, 9416L, 11009L, 9999L, 12120L, 10348L, 
15415L, 64974L, 2218L, 1329L)), class = "data.frame", row.names = c(NA, 
-33L)), vnam = "Departamento")
```

</div>
</div>




---

## cod\_dpto

<div class = "row">
<div class = "col-lg-8">

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.      26500 (5.25 %)

Number of unique values                 33

Median                                  41

1st and 3rd quartiles               15; 70

Min. and max.                        5; 99
------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-10-cod-dpto', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(5L, 10L, 15L, 20L, 25L, 
30L, 35L, 40L, 45L, 50L, 55L, 60L, 65L, 70L, 75L, 80L, 85L, 90L, 
95L), xmax = c(10L, 15L, 20L, 25L, 30L, 35L, 40L, 45L, 50L, 55L, 
60L, 65L, 70L, 75L, 80L, 85L, 90L, 95L, 100L), ymin = c(0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(67876L, 
61750L, 61370L, 31674L, 11927L, 0L, 0L, 21478L, 24181L, 37528L, 
0L, 9416L, 33477L, 15415L, 64974L, 11759L, 14852L, 6936L, 3547L
)), class = "data.frame", row.names = c(NA, -19L)), vnam = "cod_dpto")
```

</div>
</div>


- The following suspected missing value codes enter as regular values: \"99\". 



---

## Sexo

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type               character

Number of missing obs.        0 (0 %)

Number of unique values             2

Mode                          "Mujer"
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-11-Sexo', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Hombre", 
"Mujer"), class = "factor"), y = c(245029L, 259631L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Sexo")
```

</div>
</div>




---

## Grupo\_Decenal\_Edad

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type               character

Number of missing obs.        0 (0 %)

Number of unique values            10

Mode                        "[10,20)"
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-12-Grupo-Decenal-Edad', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:10, levels = c("[0,10)", 
"[10,20)", "[20,30)", "[30,40)", "[40,50)", "[50,60)", "[60,70)", 
"[70,80)", "[80,90)", "[90 y más)"), class = "factor"), y = c(82917L, 
94674L, 75737L, 68028L, 62692L, 54509L, 35658L, 20554L, 8441L, 
1450L)), class = "data.frame", row.names = c(NA, -10L)), vnam = "Grupo_Decenal_Edad")
```

</div>
</div>




---

## Regimen\_Afiliacion\_p6100

<div class = "row">
<div class = "col-lg-8">

---------------------------------------------------
Feature                                      Result
------------------------- -------------------------
Variable type                             character

Number of missing obs.               31875 (6.32 %)

Number of unique values                           4

Mode                        "2. Subsidiado (eps-s)"
---------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-13-Regimen-Afiliacion-p6100', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("1. Contributivo (EPS)", 
"2. Subsidiado (eps-s)", "3. Especial (fuerzas armadas, ecopetrol, universidades públicas", 
"4. No sabe, no informa"), class = "factor"), y = c(170668L, 
288733L, 12541L, 843L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Regimen_Afiliacion_p6100")
```

</div>
</div>




---

## Departamento\_Co

<div class = "row">
<div class = "col-lg-8">

------------------------------------------------------
Feature                                         Result
------------------------- ----------------------------
Variable type                                character

Number of missing obs.                         0 (0 %)

Number of unique values                             34

Mode                        "Valle del Cauca Colombia"
------------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-14-Departamento-Co', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:34, levels = c("Amazonas Colombia", 
"Antioquía Colombia", "Arauca Colombia", "Atlántico Colombia", 
"Bogotá Colombia", "Bolívar Colombia", "Boyacá Colombia", 
"Caldas Colombia", "Caquetá Colombia", "Casanare Colombia", 
"Cauca Colombia", "Cesar Colombia", "Choco Colombia", "Córdoba Colombia", 
"Cundinamarca Colombia", "Guainía  Colombia", "Guaviare Colombia", 
"Huila Colombia", "La Guajira Colombia", "Magdalena Colombia", 
"Meta Colombia", "NA Colombia", "Nariño Colombia", "Norte de Santander Colombia", 
"Putumayo Colombia", "Quindío Colombia", "Risaralda Colombia", 
"San Andrés, Providencia y Santa Catalina Colombia", "Santander Colombia", 
"Sucre Colombia", "Tolima Colombia", "Valle del Cauca Colombia", 
"Vaupés Colombia", "Vichada Colombia"), class = "factor"), y = c(3202L, 
51593L, 5920L, 16283L, 32108L, 14424L, 15218L, 13139L, 9299L, 
5839L, 27269L, 11663L, 11927L, 14674L, 17000L, 735L, 2999L, 12772L, 
8706L, 13183L, 10998L, 26500L, 26442L, 11086L, 4853L, 9416L, 
11009L, 9999L, 12120L, 10348L, 15415L, 64974L, 2218L, 1329L)), class = "data.frame", row.names = c(NA, 
-34L)), vnam = "Departamento_Co")
```

</div>
</div>




---

## Quintil\_Ingreso\_Percapita

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                 character

Number of missing obs.          0 (0 %)

Number of unique values               5

Mode                        "Quintil 4"
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-15-Quintil-Ingreso-Percapita', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:5, levels = c("Quintil 1", 
"Quintil 2", "Quintil 3", "Quintil 4", "Quintil 5"), class = "factor"), 
    y = c(98934L, 100647L, 101684L, 102279L, 101116L)), class = "data.frame", row.names = c(NA, 
-5L)), vnam = "Quintil_Ingreso_Percapita")
```

</div>
</div>




---

## Quintil\_Ingreso\_Percapita\_Clase

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                 character

Number of missing obs.          0 (0 %)

Number of unique values               5

Mode                        "Quintil 2"
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-16-Quintil-Ingreso-Percapita-Clase', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:5, levels = c("Quintil 1", 
"Quintil 2", "Quintil 3", "Quintil 4", "Quintil 5"), class = "factor"), 
    y = c(100017L, 101531L, 100948L, 101338L, 100826L)), class = "data.frame", row.names = c(NA, 
-5L)), vnam = "Quintil_Ingreso_Percapita_Clase")
```

</div>
</div>




---

## fex\_c

<div class = "row">
<div class = "col-lg-8">

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                      numeric

Number of missing obs.             0 (0 %)

Number of unique values              87023

Median                              343.03

1st and 3rd quartiles       151.07; 747.89

Min. and max.                2.43; 9401.79
------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-17-fex-c', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 500, 1000, 1500, 
2000, 2500, 3000, 3500, 4000, 4500, 5000, 5500, 6000, 6500, 7000, 
7500, 8000, 8500, 9000), xmax = c(500, 1000, 1500, 2000, 2500, 
3000, 3500, 4000, 4500, 5000, 5500, 6000, 6500, 7000, 7500, 8000, 
8500, 9000, 9500), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(318185L, 94398L, 44406L, 22697L, 
12967L, 6618L, 2618L, 1000L, 642L, 361L, 336L, 212L, 117L, 38L, 
41L, 8L, 8L, 0L, 8L)), class = "data.frame", row.names = c(NA, 
-19L)), vnam = "fex_c")
```

</div>
</div>


- Note that the following possible outlier values were detected: \"4086.63\", \"4092.87\", \"4095.38\", \"4113.64\", \"4113.96\", ..., \"7391.16\", \"7682.32\", \"7860.04\", \"8008.04\", \"9401.79\" (268 values omitted). 



---

## Accion\_Tratar\_enfermedad\_P8563

<div class = "row">
<div class = "col-lg-8">

-----------------------------------------------------------------------------------
Feature                                                                      Result
------------------------- ---------------------------------------------------------
Variable type                                                             character

Number of missing obs.                                              467811 (92.7 %)

Number of unique values                                                           8

Mode                        "Acudió a Institución prestadora de servicios de salud"
-----------------------------------------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-18-Accion-Tratar-enfermedad-P8563', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:8, levels = c("Acudió a Institución prestadora de servicios de salud", 
"Acudió a un boticario, farmaceuta, droguista", "Acudió de forma particular a un médico general, especialista, odontólogo, terapeuta o profesional de la salud", 
"Asistió a terapias alternativas (acupuntura, esencias florales, musicoterapia, homeopatía, etc.)", 
"Autorecetado", "Consultó a un empírico, curandero, yerbatero, comadrona", 
"No hizo nada", "Usó remedios caseros"), class = "factor"), 
    y = c(22640L, 2252L, 3023L, 101L, 3796L, 228L, 1041L, 3768L
    )), class = "data.frame", row.names = c(NA, -8L)), vnam = "Accion_Tratar_enfermedad_P8563")
```

</div>
</div>




---

## Accion\_Tratar\_enfermedad\_agregada\_P8563

<div class = "row">
<div class = "col-lg-8">

------------------------------------------------
Feature                                   Result
------------------------- ----------------------
Variable type                          character

Number of missing obs.           467811 (92.7 %)

Number of unique values                        3

Mode                        "Médica Profesional"
------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-19-Accion-Tratar-enfermedad-agregada-P8563', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:3, levels = c("Boticario, Medicina alternativa, remedios caseros, autorecetado", 
"Médica Profesional", "No hizo nada"), class = "factor"), y = c(10145L, 
25663L, 1041L)), class = "data.frame", row.names = c(NA, -3L)), 
    vnam = "Accion_Tratar_enfermedad_agregada_P8563")
```

</div>
</div>




---

## No\_Asistencia\_Razon\_p6153

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      491980 (97.49 %)

Number of unique values                   13

Mode                             "Caso leve"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-20-No-Asistencia-Razon-p6153', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:13, levels = c("Caso leve", 
"Centro de atención lejano", "Dificultad para viajar", "Espera demasiado prolongada", 
"Falta de dinero", "Falta de tiempo", "Mal servicio o cita distanciada en el tiempo", 
"Muchos trámites para la cita", "No confianza en los médicos", 
"No cubierto o autorizado por el seguro", "No lo atendieron", 
"Otro", "Problema no resuelto previamente"), class = "factor"), 
    y = c(7014L, 766L, 131L, 486L, 1070L, 227L, 1101L, 584L, 
    440L, 86L, 194L, 306L, 275L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "No_Asistencia_Razon_p6153")
```

</div>
</div>




---

## No\_Asistencia\_Agregada\_p6153

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      491569 (97.41 %)

Number of unique values                    2

Mode                               "Demanda"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-21-No-Asistencia-Agregada-p6153', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Demanda", 
"Oferta"), class = "factor"), y = c(9026L, 4065L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "No_Asistencia_Agregada_p6153")
```

</div>
</div>




---

## No\_Afiliacion\_Razon\_p768

<div class = "row">
<div class = "col-lg-8">

---------------------------------------------------
Feature                                      Result
------------------------- -------------------------
Variable type                             character

Number of missing obs.             480195 (95.15 %)

Number of unique values                           8

Mode                        "Afiliación en trámite"
---------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-22-No-Afiliacion-Razon-p768', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:8, levels = c("Afiliación en trámite", 
"Desconocimiento", "Entidad cercana no disponible", "Falta de dinero", 
"No interesa", "No vinculado laboralmente", "Otras razones", 
"Trámites complejos"), class = "factor"), y = c(7018L, 537L, 
381L, 2988L, 3782L, 2958L, 3234L, 3567L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "No_Afiliacion_Razon_p768")
```

</div>
</div>




---

## Dias\_incapacidad\_p6134

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                        numeric

Number of missing obs.      459922 (91.14 %)

Number of unique values                   70

Median                                     2

1st and 3rd quartiles                   0; 7

Min. and max.                         0; 120
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-23-Dias-incapacidad-p6134', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 10, 20, 30, 40, 50, 
60, 70, 80, 90, 100, 110), xmax = c(10, 20, 30, 40, 50, 60, 70, 
80, 90, 100, 110, 120), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(38747L, 3410L, 1328L, 68L, 79L, 228L, 5L, 8L, 
144L, 574L, 2L, 145L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "Dias_incapacidad_p6134")
```

</div>
</div>


- Note that the following possible outlier values were detected: \"55\", \"56\", \"58\", \"60\", \"67\", ..., \"105\", \"110\", \"112\", \"119\", \"120\" (12 values omitted). 



---

## Ocupacion\_p6240

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      102042 (20.22 %)

Number of unique values                    6

Mode                            "Trabajando"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-24-Ocupacion-p6240', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:6, levels = c("Buscando trabajo", 
"Estudiando", "Incapacitado permanentemente para trabajar", "Oficios del hogar", 
"Otra actividad", "Trabajando"), class = "factor"), y = c(12416L, 
63667L, 11975L, 109733L, 17879L, 186948L)), class = "data.frame", row.names = c(NA, 
-6L)), vnam = "Ocupacion_p6240")
```

</div>
</div>




---

## Ocupacion\_Posicion\_p6435

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------------------------------------
Feature                                                             Result
------------------------- ------------------------------------------------
Variable type                                                    character

Number of missing obs.                                       287670 (57 %)

Number of unique values                                                 10

Mode                        "Trabajador independiente o por cuenta propia"
--------------------------------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-25-Ocupacion-Posicion-p6435', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:10, levels = c("Ayudante sin remuneracion (hijo o familiar de empleados domésticos...)", 
"Empleado doméstico", "Jornalero de peón", "Obrero o empleado de empresa particular", 
"Obrero o empleado del gobierno", "Patrón o empleado", "Profesional independiente", 
"Trabajador de finca, tierra o parcela propia en arriendo, ap", 
"Trabajador independiente o por cuenta propia", "Trabajador sin remuneración"
), class = "factor"), y = c(1195L, 5184L, 11866L, 71344L, 10817L, 
6574L, 3409L, 12627L, 88698L, 5276L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "Ocupacion_Posicion_p6435")
```

</div>
</div>




---

## Estado\_salud\_general\_P6127

<div class = "row">
<div class = "col-lg-8">

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                character

Number of missing obs.         0 (0 %)

Number of unique values              4

Mode                        "2. Bueno"
--------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-26-Estado-salud-general-P6127', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("1. Muy bueno", 
"2. Bueno", "3. Regular", "4. Malo"), class = "factor"), y = c(50281L, 
349725L, 95540L, 9114L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Estado_salud_general_P6127")
```

</div>
</div>




---

## calidad\_Atencion\_Prevencion\_P8595

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      301123 (59.67 %)

Number of unique values                    4

Mode                                 "Buena"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-27-calidad-Atencion-Prevencion-P8595', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("Buena", 
"Mala", "Muy buena", "Muy Mala"), class = "factor"), y = c(170135L, 
17563L, 14786L, 1053L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "calidad_Atencion_Prevencion_P8595")
```

</div>
</div>




---

## Enfermedad\_Ultimo\_mes\_P5665

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type               character

Number of missing obs.        0 (0 %)

Number of unique values             2

Mode                             "No"
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-28-Enfermedad-Ultimo-mes-P5665', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(459922L, 44738L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Enfermedad_Ultimo_mes_P5665")
```

</div>
</div>




---

## Cubrir\_Costos\_Atención\_Salud\_EPS\_p8556s1

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------------------------------------------
Feature                                                                   Result
------------------------- ------------------------------------------------------
Variable type                                                          character

Number of missing obs.                                          459922 (91.14 %)

Number of unique values                                                        2

Mode                        "Entidad de seguridad social de la cual es afiliado"
--------------------------------------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-29-Cubrir-Costos-Atencion-Salud-EPS-p8556s1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Entidad de seguridad social de la cual es afiliado", 
"Otros"), class = "factor"), y = c(26247L, 18491L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Cubrir_Costos_Atención_Salud_EPS_p8556s1")
```

</div>
</div>




---

## Cubrir\_Costos\_Atencion\_Salud\_Seguro\_Voluntario\_p8556s2

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      459922 (91.14 %)

Number of unique values                    2

Mode                                 "Otros"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-30-Cubrir-Costos-Atencion-Salud-Seguro-Voluntario-p8556s2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Otros", 
"Seguro médico, plan complementario o medicina prepagada"), class = "factor"), 
    y = c(44367L, 371L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Cubrir_Costos_Atencion_Salud_Seguro_Voluntario_p8556s2")
```

</div>
</div>




---

## Cubrir\_Costos\_Atencion\_Salud\_Seguro\_Obligatorio\_p8556s4

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      459922 (91.14 %)

Number of unique values                    2

Mode                                 "Otros"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-31-Cubrir-Costos-Atencion-Salud-Seguro-Obligatorio-p8556s4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Otros", 
"Seguro obligatorio de accidentes de tránsito (SOAT)"), class = "factor"), 
    y = c(44504L, 234L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Cubrir_Costos_Atencion_Salud_Seguro_Obligatorio_p8556s4")
```

</div>
</div>




---

## Cubrir\_Costos\_Atencion\_Salud\_Alcaldia\_p8556s5

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      459922 (91.14 %)

Number of unique values                    2

Mode                                 "Otros"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-32-Cubrir-Costos-Atencion-Salud-Alcaldia-p8556s5', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Otros", 
"Secretaría de salud o la alcaldía"), class = "factor"), y = c(44560L, 
178L)), class = "data.frame", row.names = c(NA, -2L)), vnam = "Cubrir_Costos_Atencion_Salud_Alcaldia_p8556s5")
```

</div>
</div>




---

## Cubrir\_Costos\_Atencion\_Salud\_Propios\_familiares\_p8556s6

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      459922 (91.14 %)

Number of unique values                    2

Mode                                 "Otros"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-33-Cubrir-Costos-Atencion-Salud-Propios-familiares-p8556s6', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Otros", 
"Recursos propios y/o familiares"), class = "factor"), y = c(38174L, 
6564L)), class = "data.frame", row.names = c(NA, -2L)), vnam = "Cubrir_Costos_Atencion_Salud_Propios_familiares_p8556s6")
```

</div>
</div>




---

## Cubrir\_Costos\_Atencion\_Salud\_Otras\_Personas\_p8556s9

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      459922 (91.14 %)

Number of unique values                    2

Mode                                 "Otros"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-34-Cubrir-Costos-Atencion-Salud-Otras-Personas-p8556s9', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Otros", 
"Recursos de otras personas"), class = "factor"), y = c(44389L, 
349L)), class = "data.frame", row.names = c(NA, -2L)), vnam = "Cubrir_Costos_Atencion_Salud_Otras_Personas_p8556s9")
```

</div>
</div>




---

## Cubrir\_Costos\_Atencion\_Salud\_No\_Requiere\_p8556s10

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      459922 (91.14 %)

Number of unique values                    2

Mode                                 "Otros"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-35-Cubrir-Costos-Atencion-Salud-No-Requiere-p8556s10', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No se requirió pago", 
"Otros"), class = "factor"), y = c(198L, 44540L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Cubrir_Costos_Atencion_Salud_No_Requiere_p8556s10")
```

</div>
</div>




---

## Percepcion\_Calidad\_Entidad\_p6181

<div class = "row">
<div class = "col-lg-8">

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                    character

Number of missing obs.      32718 (6.48 %)

Number of unique values                  5

Mode                            "2. Bueno"
------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-36-Percepcion-Calidad-Entidad-p6181', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:5, levels = c("1. Muy bueno", 
"2. Bueno", "3. Mala", "4. Muy Mala", "5. No Sabe"), class = "factor"), 
    y = c(26717L, 350158L, 72270L, 12262L, 10535L)), class = "data.frame", row.names = c(NA, 
-5L)), vnam = "Percepcion_Calidad_Entidad_p6181")
```

</div>
</div>




---

## Percepcion\_Calidad\_Entidad\_Factor\_P798

<div class = "row">
<div class = "col-lg-8">

---------------------------------------------
Feature                                Result
------------------------- -------------------
Variable type                       character

Number of missing obs.       444192 (88.02 %)

Number of unique values                     7

Mode                        "Demora en citas"
---------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-37-Percepcion-Calidad-Entidad-Factor-P798', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:7, levels = c("Demora en atención médica", 
"Demora en citas", "Falta capacidad médica", "Infraestructura", 
"Mala atención", "Otro", "Trámites excesivos"), class = "factor"), 
    y = c(4837L, 28088L, 1605L, 1651L, 12624L, 1384L, 10279L)), class = "data.frame", row.names = c(NA, 
-7L)), vnam = "Percepcion_Calidad_Entidad_Factor_P798")
```

</div>
</div>




---

## Percepcion\_Calidad\_Prestacion\_p8554

* The variable only takes one value: \"NA\".



---

## Percepcion\_Calidad\_Prestacion\_Factor\_P801

<div class = "row">
<div class = "col-lg-8">

------------------------------------------------------------------------------------------
Feature                                                                             Result
------------------------- ----------------------------------------------------------------
Variable type                                                                    character

Number of missing obs.                                                    502075 (99.49 %)

Number of unique values                                                                  8

Mode                        "Mala atención del personal administrativo o asistencial (méd"
------------------------------------------------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-39-Percepcion-Calidad-Prestacion-Factor-P801', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:8, levels = c("Condiciones deficientes de infraestructura, dotación o mobil", 
"Demora en la asignación de citas", "Demora en la atención por parte del personal médico", 
"Falta de capacidad, conocimientos o habilidad del personal a", 
"Mala atención del personal administrativo o asistencial (méd", 
"Otro", "Problemas relacionados con los medicamentos", "Trámites excesivos o dispendiosos"
), class = "factor"), y = c(53L, 423L, 668L, 219L, 771L, 63L, 
75L, 313L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "Percepcion_Calidad_Prestacion_Factor_P801")
```

</div>
</div>




---

## Percepcion\_pobreza\_p5230

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                 character

Number of missing obs.      73 (0.01 %)

Number of unique values               2

Mode                               "No"
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-40-Percepcion-pobreza-p5230', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(277428L, 227159L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Percepcion_pobreza_p5230")
```

</div>
</div>




---

## Percepcion\_suficiencia\_ingresos\_p9090

<div class = "row">
<div class = "col-lg-8">

----------------------------------------------------------------
Feature                                                   Result
------------------------- --------------------------------------
Variable type                                          character

Number of missing obs.                               73 (0.01 %)

Number of unique values                                        3

Mode                        "Alcanza para cubrir gastos mínimos"
----------------------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-41-Percepcion-suficiencia-ingresos-p9090', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:3, levels = c("Alcanza para cubrir gastos mínimos", 
"Cubre más que gastos mínimos", "No alcanza para cubrir gastos mínimos"
), class = "factor"), y = c(284323L, 42112L, 178152L)), class = "data.frame", row.names = c(NA, 
-3L)), vnam = "Percepcion_suficiencia_ingresos_p9090")
```

</div>
</div>




---

## Quejas\_Ultimo\_Ano

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      320834 (63.57 %)

Number of unique values                    2

Mode                                    "No"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-42-Quejas-Ultimo-Ano', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(167368L, 16458L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Quejas_Ultimo_Ano")
```

</div>
</div>




---

## Tutelas\_Ultimo\_Ano

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                 character

Number of missing obs.      73 (0.01 %)

Number of unique values               2

Mode                               "No"
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-43-Tutelas-Ultimo-Ano', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(496591L, 7996L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Tutelas_Ultimo_Ano")
```

</div>
</div>




---

## Tutelas\_Ultimo\_Ano\_razon

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------------------------------------
Feature                                                             Result
------------------------- ------------------------------------------------
Variable type                                                    character

Number of missing obs.                                    496664 (98.42 %)

Number of unique values                                                  7

Mode                        "No lo atendieron en una institución de salud"
--------------------------------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-44-Tutelas-Ultimo-Ano-razon', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:7, levels = c("Le negaron el cambio de régimen de afiliación a salud.", 
"No está afiliado al sistema general de seguridad social en s", 
"No está de acuerdo con el nivel de sisben asignado", "No le dieron los medicamentos", 
"No lo atendieron en una institución de salud", "No tiene dinero para pagar un tratamiento", 
"Otra"), class = "factor"), y = c(84L, 116L, 51L, 2528L, 2570L, 
994L, 1653L)), class = "data.frame", row.names = c(NA, -7L)), 
    vnam = "Tutelas_Ultimo_Ano_razon")
```

</div>
</div>




---

## Cronica\_Diagnostico\_p1930

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      391750 (77.63 %)

Number of unique values                    2

Mode                                    "No"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-45-Cronica-Diagnostico-p1930', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(97012L, 15898L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Cronica_Diagnostico_p1930")
```

</div>
</div>




---

## Cronica\_Tratamiento\_p1930s1

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      488762 (96.85 %)

Number of unique values                    2

Mode                                    "Sí"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-46-Cronica-Tratamiento-p1930s1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(1837L, 14061L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Cronica_Tratamiento_p1930s1")
```

</div>
</div>




---

## Discapacidad\_Oir\_p1906s1

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      365250 (72.38 %)

Number of unique values                    4

Mode                        "Sin dificultad"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-47-Discapacidad-Oir-p1906s1', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("No puede hacerlo", 
"Sí, con alguna dificultad", "Sí, con mucha dificultad", "Sin dificultad"
), class = "factor"), y = c(272L, 4158L, 1339L, 133641L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Discapacidad_Oir_p1906s1")
```

</div>
</div>




---

## Consulta\_Prevencion\_Medico

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      290901 (57.64 %)

Number of unique values                    2

Mode                                    "Si"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-48-Consulta-Prevencion-Medico', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Si"), class = "factor"), y = c(73246L, 140513L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Consulta_Prevencion_Medico")
```

</div>
</div>




---

## Consulta\_Prevencion\_Odontologo

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      290901 (57.64 %)

Number of unique values                    2

Mode                                    "Si"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-49-Consulta-Prevencion-Odontologo', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Si"), class = "factor"), y = c(97481L, 116278L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Consulta_Prevencion_Odontologo")
```

</div>
</div>




---

## Consulta\_Prevencion\_Medico\_Odontologo

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------------------
Feature                                          Result
------------------------- -----------------------------
Variable type                                 character

Number of missing obs.                 213759 (42.36 %)

Number of unique values                               4

Mode                        "Al médico y al odontólogo"
-------------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-50-Consulta-Prevencion-Medico-Odontologo', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("A ninguno", 
"Al médico y al odontólogo", "Sólo al médico", "Sólo al odontólogo"
), class = "factor"), y = c(93950L, 100840L, 79322L, 16789L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Consulta_Prevencion_Medico_Odontologo")
```

</div>
</div>




---

## Discapacidad\_Hablar\_p1906s2

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      365250 (72.38 %)

Number of unique values                    4

Mode                        "Sin dificultad"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-51-Discapacidad-Hablar-p1906s2', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("No puede hacerlo", 
"Sí, con alguna dificultad", "Sí, con mucha dificultad", "Sin dificultad"
), class = "factor"), y = c(812L, 1569L, 759L, 136270L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Discapacidad_Hablar_p1906s2")
```

</div>
</div>




---

## Discapacidad\_Ver\_p1906s3

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      365250 (72.38 %)

Number of unique values                    4

Mode                        "Sin dificultad"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-52-Discapacidad-Ver-p1906s3', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("No puede hacerlo", 
"Sí, con alguna dificultad", "Sí, con mucha dificultad", "Sin dificultad"
), class = "factor"), y = c(232L, 23571L, 6657L, 108950L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Discapacidad_Ver_p1906s3")
```

</div>
</div>




---

## Discapacidad\_Moverse\_Caminar\_p1906s4

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      365250 (72.38 %)

Number of unique values                    4

Mode                        "Sin dificultad"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-53-Discapacidad-Moverse-Caminar-p1906s4', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("No puede hacerlo", 
"Sí, con alguna dificultad", "Sí, con mucha dificultad", "Sin dificultad"
), class = "factor"), y = c(816L, 6551L, 2780L, 129263L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Discapacidad_Moverse_Caminar_p1906s4")
```

</div>
</div>




---

## Discapacidad\_Usar\_Manos\_p1906s5

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      365250 (72.38 %)

Number of unique values                    4

Mode                        "Sin dificultad"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-54-Discapacidad-Usar-Manos-p1906s5', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("No puede hacerlo", 
"Sí, con alguna dificultad", "Sí, con mucha dificultad", "Sin dificultad"
), class = "factor"), y = c(348L, 3085L, 1094L, 134883L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Discapacidad_Usar_Manos_p1906s5")
```

</div>
</div>




---

## Discapacidad\_Entender\_p1906s6

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      365250 (72.38 %)

Number of unique values                    4

Mode                        "Sin dificultad"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-55-Discapacidad-Entender-p1906s6', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("No puede hacerlo", 
"Sí, con alguna dificultad", "Sí, con mucha dificultad", "Sin dificultad"
), class = "factor"), y = c(1066L, 2659L, 984L, 134701L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Discapacidad_Entender_p1906s6")
```

</div>
</div>




---

## Discapacidad\_Comer\_Vestirse\_Bañarse\_Solo\_p1906s7

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      365250 (72.38 %)

Number of unique values                    4

Mode                        "Sin dificultad"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-56-Discapacidad-Comer-Vestirse-Banarse-Solo-p1906s7', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("No puede hacerlo", 
"Sí, con alguna dificultad", "Sí, con mucha dificultad", "Sin dificultad"
), class = "factor"), y = c(1236L, 1240L, 483L, 136451L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Discapacidad_Comer_Vestirse_Bañarse_Solo_p1906s7")
```

</div>
</div>




---

## Discapacidad\_Relacionarse\_p1906s8

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      365250 (72.38 %)

Number of unique values                    4

Mode                        "Sin dificultad"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-57-Discapacidad-Relacionarse-p1906s8', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:4, levels = c("No puede hacerlo", 
"Sí, con alguna dificultad", "Sí, con mucha dificultad", "Sin dificultad"
), class = "factor"), y = c(691L, 1154L, 535L, 137030L)), class = "data.frame", row.names = c(NA, 
-4L)), vnam = "Discapacidad_Relacionarse_p1906s8")
```

</div>
</div>




---

## Dias\_Cita\_consulta\_Acudio\_especialista\_p6199

* The variable only takes one value: \"NA\".



---

## Dias\_Cita\_consulta\_Medico\_p6199

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                       numeric

Number of missing obs.      490020 (97.1 %)

Number of unique values                  28

Median                                    1

1st and 3rd quartiles                  0; 3

Min. and max.                         0; 30
-------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-59-Dias-Cita-consulta-Medico-p6199', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28), xmax = c(2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28, 30), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(10584L, 1487L, 443L, 
1025L, 126L, 35L, 15L, 376L, 9L, 139L, 5L, 4L, 14L, 5L, 373L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "Dias_Cita_consulta_Medico_p6199")
```

</div>
</div>




---

## Dias\_Cita\_consulta\_Odontologo\_p6199

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                        numeric

Number of missing obs.      503313 (99.73 %)

Number of unique values                   21

Median                                     1

1st and 3rd quartiles                   0; 3

Min. and max.                          0; 30
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-60-Dias-Cita-consulta-Odontologo-p6199', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28), xmax = c(2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28, 30), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(931L, 133L, 34L, 123L, 
18L, 3L, 1L, 40L, 1L, 16L, 0L, 0L, 1L, 1L, 45L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "Dias_Cita_consulta_Odontologo_p6199")
```

</div>
</div>




---

## Algun\_miembro\_Hogar\_No\_Consumio\_Ninguna\_Comida\_Un\_Dia\_O\_Mas\_p8706

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                     character

Number of missing obs.      74240 (14.71 %)

Number of unique values                   2

Mode                                   "No"
-------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-61-Algun-miembro-Hogar-No-Consumio-Ninguna-Comida-Un-Dia-O-Mas-p8706', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(405546L, 24874L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Algun_miembro_Hogar_No_Consumio_Ninguna_Comida_Un_Dia_O_Mas_p8706")
```

</div>
</div>




---

## Controles\_Crecimiento\_Desarrollo\_p6161

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      491947 (97.48 %)

Number of unique values                    2

Mode                                    "Sí"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-62-Controles-Crecimiento-Desarrollo-p6161', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(1296L, 11417L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Controles_Crecimiento_Desarrollo_p6161")
```

</div>
</div>




---

## Controles\_Crecimiento\_Desarrollo\_numero\_p6161

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                        numeric

Number of missing obs.      493243 (97.74 %)

Number of unique values                   18

Median                                     2

1st and 3rd quartiles                   2; 3

Min. and max.                          1; 24
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-63-Controles-Crecimiento-Desarrollo-numero-p6161', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22), xmax = c(2, 4, 6, 8, 10, 12, 14, 16, 18, 
20, 22, 24), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(7048L, 
3516L, 612L, 105L, 52L, 72L, 2L, 5L, 0L, 1L, 0L, 4L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "Controles_Crecimiento_Desarrollo_numero_p6161")
```

</div>
</div>


- Note that the following possible outlier values were detected: \"1\". 



---

## Alfabeta\_p6160

<div class = "row">
<div class = "col-lg-8">

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                    character

Number of missing obs.      38476 (7.62 %)

Number of unique values                  2

Mode                                  "Sí"
------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-64-Alfabeta-p6160', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(39474L, 426710L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Alfabeta_p6160")
```

</div>
</div>




---

## Asiste\_Educacion\_p8586

<div class = "row">
<div class = "col-lg-8">

------------------------------------------
Feature                             Result
------------------------- ----------------
Variable type                    character

Number of missing obs.      38476 (7.62 %)

Number of unique values                  2

Mode                                  "No"
------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-65-Asiste-Educacion-p8586', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Sí"), class = "factor"), y = c(328655L, 137529L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Asiste_Educacion_p8586")
```

</div>
</div>




---

## Razon\_No\_Estudio\_p6218

<div class = "row">
<div class = "col-lg-8">

-----------------------------------------------
Feature                                  Result
------------------------- ---------------------
Variable type                         character

Number of missing obs.         390923 (77.46 %)

Number of unique values                      15

Mode                        "Necesita trabajar"
-----------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-66-Razon-No-Estudio-p6218', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:15, levels = c("Cambio de residencia", 
"Considera que no está en edad escolar", "Considera que ya terminó", 
"Costo elevado o falta de dinero", "Debe encargarse del hogar", 
"Educación especial", "Inseguridad o malos tratos en el establecimiento educativo", 
"Necesita trabajar", "No existe centro educativo cercano", "No le gusta o no interesa el estudio", 
"Otros", "Por embarazo", "Por enfermedad", "Por situaciones académicas (bajos resultados en el periodo académico, repetición de cursos", 
"Sus padres no lo consideran importante"), class = "factor"), 
    y = c(1330L, 3429L, 13505L, 23789L, 14820L, 1133L, 387L, 
    33684L, 1808L, 12164L, 3202L, 2756L, 1531L, 2L, 197L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "Razon_No_Estudio_p6218")
```

</div>
</div>


- Note that the following levels have at most five observations: \"Por situaciones académicas (bajos resultados en el periodo académico, repetición de cursos\". 



---

## Razon\_No\_Estudio\_Agregada\_p6218

<div class = "row">
<div class = "col-lg-8">

---------------------------------------------
Feature                                Result
------------------------- -------------------
Variable type                       character

Number of missing obs.       390923 (77.46 %)

Number of unique values                     2

Mode                        "Barreras_Acceso"
---------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-67-Razon-No-Estudio-Agregada-p6218', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("Barreras_Acceso", 
"Razones_Personales"), class = "factor"), y = c(83309L, 30428L
)), class = "data.frame", row.names = c(NA, -2L)), vnam = "Razon_No_Estudio_Agregada_p6218")
```

</div>
</div>




---

## Nivel\_Educativo\_Actual\_p8587

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      176005 (34.88 %)

Number of unique values                   13

Mode                              "Primaria"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-68-Nivel-Educativo-Actual-p8587', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:13, levels = c("Media", 
"Ninguno", "Posgrado con título", "Posgrado sin título", "Preescolar", 
"Primaria", "Secundaria", "Técnico con título", "Técnico sin título", 
"Tecnológico con título", "Tecnológico sin título", "Universitaria con título", 
"Universitaria sin título"), class = "factor"), y = c(78997L, 
27234L, 5418L, 220L, 742L, 116648L, 50564L, 17768L, 2003L, 6633L, 
851L, 17805L, 3772L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "Nivel_Educativo_Actual_p8587")
```

</div>
</div>




---

## Nivel\_Educativo\_Alcanzado\_p1088

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      367131 (72.75 %)

Number of unique values                    8

Mode                              "Primaria"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-69-Nivel-Educativo-Alcanzado-p1088', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:8, levels = c("Media", 
"Postgrado", "Preescolar", "Primaria", "Secundaria", "Técnico", 
"Tecnológico", "Universitario"), class = "factor"), y = c(15276L, 
1315L, 9978L, 52210L, 39227L, 5207L, 2354L, 11962L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "Nivel_Educativo_Alcanzado_p1088")
```

</div>
</div>




---

## Anos\_de\_Educacion

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          32

Median                            5

1st and 3rd quartiles         2; 11

Min. and max.                 0; 31
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-70-Anos-de-Educacion', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28, 30), xmax = c(2, 4, 6, 8, 10, 
12, 14, 16, 18, 20, 22, 24, 26, 28, 30, 32), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(137085L, 57503L, 
83993L, 43525L, 33731L, 86821L, 28976L, 20831L, 5064L, 1002L, 
1923L, 2810L, 981L, 263L, 87L, 65L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "Anos_de_Educacion")
```

</div>
</div>




---

## Anos\_de\_Educacion.jefe

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          32

Median                            0

1st and 3rd quartiles          0; 2

Min. and max.                 0; 31
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-71-Anos-de-Educacion-jefe', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28, 30), xmax = c(2, 4, 6, 8, 10, 
12, 14, 16, 18, 20, 22, 24, 26, 28, 30, 32), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(380808L, 19394L, 
30160L, 11178L, 7907L, 30497L, 9864L, 8342L, 2367L, 511L, 1052L, 
1666L, 631L, 173L, 66L, 44L)), class = "data.frame", row.names = c(NA, 
-16L)), vnam = "Anos_de_Educacion.jefe")
```

</div>
</div>




---

## Analfabetismo\_IPM

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type               character

Number of missing obs.        0 (0 %)

Number of unique values             2

Mode                             "No"
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-72-Analfabetismo-IPM', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Si"), class = "factor"), y = c(477932L, 26728L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Analfabetismo_IPM")
```

</div>
</div>




---

## Rezago\_Escolar\_IPM

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      399906 (79.24 %)

Number of unique values                    2

Mode                                    "Si"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-73-Rezago-Escolar-IPM', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Si"), class = "factor"), y = c(35252L, 69502L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Rezago_Escolar_IPM")
```

</div>
</div>




---

## Inasistencia\_Escolar\_IPM

<div class = "row">
<div class = "col-lg-8">

--------------------------------------------
Feature                               Result
------------------------- ------------------
Variable type                      character

Number of missing obs.      400430 (79.35 %)

Number of unique values                    2

Mode                                    "No"
--------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-74-Inasistencia-Escolar-IPM', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, levels = c("No", 
"Si"), class = "factor"), y = c(97512L, 6718L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Inasistencia_Escolar_IPM")
```

</div>
</div>




---



Report generation information:

 *  Created by: Ilich Herbert De La Hoz Siegler (username: `ilichherbertdelahozsiegler`).

 *  Report creation time: Sat Feb 03 2024 18:19:49

 *  Report was run from directory: `/Users/ilichherbertdelahozsiegler/Desktop/prueba_adres`

 *  R version 4.3.2 (2023-10-31).

 *  Platform: aarch64-apple-darwin20 (64-bit)(America/Bogota).


